The Name of the Title is Hope

### 2023-09-15 input/2_introduction.tex
Updates from Overleaf

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{figures/bci_game.png}
    \caption{Our Augmentation system: When participants feel the spontaneous urge to move, readiness potentials (RPs) are picked up in the user's EEG signals. A brain-computer interface (BCI) predicts the data to be in either of two classes: Idle or pre-movement. In the latter case, the user's hand is moved by trigger electrical muscle stimulation (EMS). Image presented with consent from participant.}
\end{figure}

>>>>

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{figures/bci_game.png}
    \caption{Our AUGMENTATION system: When participants feel the spontaneous urge to move, readiness potentials (RPs) are picked up in the user's EEG signals. A brain-computer interface (BCI) predicts the data to be in either of two classes: Idle or pre-movement. In the latter case, the user's hand is moved by trigger electrical muscle stimulation (EMS). Image presented with consent from participant.}
\end{figure}

### 2023-09-15 input/5_user_study_and_methods.tex
Updates from Overleaf

\subsection{Experimental Task, Design and Procedure}
Participants performed a simple tapping task in three conditions with 75 trials each: INTENTION, EXTERNAL, and AUGMENTED, see figure~\ref{fig:task_design}.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{figures/setup.png}
    \label{fig:setup}
    \caption{Experimental setup of measurement-- and input devices (image with consent from participant).}
\end{figure}

@@

\subsubsection{Real-time application and EMS control}
During real-time application, the EEG data was buffered for the last second for the selected channels. The data was band-pass filtered analogously to the training data from 0.1 to 15 Hz. Next, the slope was computed for the discriminative channels selected in the classifier cross-validation grid search. This procedure ran at an update rate of 10 Hz, hence every 100 ms a new prediction was obtained from the classifier. To smooth the prediction output with the goal of reducing false predictions due to unlikely peaks, the predicted probability for the \textit{pre-movement} class was smoothed by averaging the last two predictions with a weighting (.3 and .5). Then, at 10Hz update rate, this smoothed probability, as well as the predicted class for the current frame were gating the EMS switch: when the probability exceeded the threshold and the currently predicted class was \textit{pre-movement}, the switch was opened for 0.5s.

@@

\subsection{Measures of Agency Experience: Intentional Binding, Question \& Interview}
To assess if SoA was preserved, an intentional binding measure, a standardized question, and an interview following the AUGMENTED block were investigated. At the conclusion of each condition we prompted participants to rate their experienced agency on a 7-point Likert scale with the statement ``It felt like I was in control of the movements during the task.'', the item was copied from~\cite{Hornbaek}. Following AUGMENTED we interviewed users about their experience working with the system. After prompting users to recall their experience and summarize what their task had been we set the focus to the tapping movement and asked them to ignore the time estimation task for the following questions. We entered the open part of the interview by asking: ``What did the system do?'' followed up by ``What was the difference between the three conditions''. After some time, and depending on their answers, we reset the focus to the AUGMENTED condition and asked ``How often was the system active?'' followed by ``What do you think caused the actions of the system?''. This was then followed up by an `open' interview in which we frequently asked `how' and `why' questions to inquire about the user's experience.

@@

In line with the literature on intentional binding, we hypothesized that the time intervals should be underestimated for the INTENTION and the AUGMENTED conditions. This should not be the case for the EXTERNAL condition where users had no intention to move. Hence, when binding occurs, the intervals should be underestimated, hinting at a higher SoA. To test this, we fit a linear mixed effects model with \textit{condition} (INTENTION, EXTERNAL, AUGMENTED) as a fixed effect. As a random effect, we considered the intercepts for participants. We obtained p-values of the coefficients by calculating likelihood-ratio tests~\cite{winterLinearModelsLinear2013}. All parameters were estimated by maximum likelihood estimation~\cite[see][]{Pinheiro2000}. Post-hoc, pairwise contrasts were computed using estimated marginal means with Tukey's methods for multiple comparisons corrections~\cite{Lenth2020-xk}.

>>>>

\subsection{Experimental Task, Design and Procedure}
Participants performed a simple tapping task in three conditions with 75 trials each: INTENTION, EXTERNAL, and AUGMENTED.
% , see figure~\ref{fig:task_design}.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{figures/setup.png}
    \caption{Experimental setup of measurement-- and input devices (image with consent from participant).}
    \label{fig:setup}
\end{figure}

@@

\subsubsection{Real-time application and EMS control}
During real-time application, the EEG data was buffered for the last second for the selected channels. The data was band-pass filtered analogously to the training data from 0.1 to 15 Hz. Next, the slope was computed for the discriminative channels selected in the classifier cross-validation grid search. This procedure ran at an update rate of 10 Hz, hence every 100 ms a new prediction was obtained from the classifier. To smooth the prediction output with the goal of reducing false predictions due to unlikely peaks, the predicted probability for the \textit{pre-movement} class was smoothed by averaging the last two predictions with a weighting (.3 and .5). Then, at 10 Hz update rate, this smoothed probability, as well as the predicted class for the current frame were gating the EMS switch: when the probability exceeded the threshold and the currently predicted class was \textit{pre-movement}, the switch was opened for 0.5 s.

@@

\subsection{Measures of Agency Experience: Intentional Binding, Question \& Interview}
To assess if SoA was preserved, an intentional binding measure, a standardized question, and an interview following the AUGMENTED block were investigated. At the conclusion of each condition we prompted participants to rate their experienced agency on a 7-point Likert scale with the statement ``It felt like I was in control of the movements during the task.'', the item was copied from~\cite{Bergstrom2022-fb}. Following AUGMENTED we interviewed users about their experience working with the system. After prompting users to recall their experience and summarize what their task had been we set the focus to the tapping movement and asked them to ignore the time estimation task for the following questions. We entered the open part of the interview by asking: ``What did the system do?'' followed up by ``What was the difference between the three conditions''. After some time, and depending on their answers, we reset the focus to the AUGMENTED condition and asked ``How often was the system active?'' followed by ``What do you think caused the actions of the system?''. This was then followed up by an `open' interview in which we frequently asked `how' and `why' questions to inquire about the user's experience.

@@

In line with the literature on intentional binding, we hypothesized that the time intervals should be underestimated for the INTENTION and the AUGMENTED conditions. This should not be the case for the EXTERNAL condition where users had no intention to move. Hence, when binding occurs, the intervals should be underestimated, hinting at a higher SoA. To test this, we fit a linear mixed effects model with \textit{condition} (INTENTION, EXTERNAL, AUGMENTED) as a fixed effect. As a random effect, we considered the intercepts for participants. We obtained p-values of the coefficients by calculating likelihood-ratio tests. All parameters were estimated by maximum likelihood estimation~\cite[see][]{Pinheiro2006-bk}. Post-hoc, pairwise contrasts were computed using estimated marginal means with Tukey's methods for multiple comparisons corrections~\cite{Lenth2020-xk}.
% ~\cite{winterLinearModelsLinear2013}
